%-------------------------------------------------------------------------------
%	SECTION TITLE
%-------------------------------------------------------------------------------
\cvsection{Projects}

\begin{cventries}

     \cventry
    {C, C++} % Role
    {VI like text editor for Linux/Unix based Systems.} % Title
    {} % Location
    {} % Date(s)
    {
      \begin{cvitems} % Description(s)
        \item {A Text editor for Linux/Unix with text and command handling capabilities.}
        \item {Use of different Data Structures for performance analysis.(eg. Gap Buffers, Vectors of Link list etc.)}
      \end{cvitems}
    }
    
    \cventry
    {Java, Information Retrieval, Data Engineering} % Role
    {Wikipedia - Information Retrieval} % Title
    {} % Location
    {} % Date(s)
    {
      \begin{cvitems} % Description(s)
        \item {Creation of search model based on TF-IDF Ranking with defined weights on indexing fields.}
        \item {Query Processing in full text search results into top 10 titles of documents ranked in ascending order.}
      \end{cvitems}
    }
    
    \cventry
    {NodeJS, MongoDB, Bootstrap} % Role
    {Splitwise Application.} % Title
    {} % Location
    {} % Date(s)
    {
      \begin{cvitems} % Description(s)
        \item {An application for splitting up and settling bills between people.}
      \end{cvitems}
    }
    
     \cventry
    {C/C++, Socket Programming, Remote Procedure Call} % Role
    {Hybrid P2P File Sharing, Torrent like system} % Title
    {} % Location
    {} % Date(s)
    {
      \begin{cvitems} % Description(s)
        \item {Local Peer to Peer file sharing system for locally connected systems.}
        \item {Remote procedure calls on other systems.}
      \end{cvitems}
    }
    

    
    \cventry
    {Python, NLP, Machine Learning} % Role
    {Grammatical Error Correction and Sentence Completion.} % Title
    {} % Location
    {} % Date(s)
    {
      \begin{cvitems} % Description(s)
        \item {Used standard NLP techniques like Hidden Markov Model, POS tagging for sentence completion and a mixture of techniques like Naive Bayes, Logestic Regression and Edit Distance for grammatical error Detection, Classification \& Correction.}
      \end{cvitems}
    }
    
    
    
    \cventry
    {Python, Machine Learning, Data Engineering} % Role
    {Sentimental analysis on Movie Review and News Datasets} % Title
    {} % Location
    {} % Date(s)
    {
      \begin{cvitems} % Description(s)
        \item {Sentimental classification of articles using SVM and Random Forest Methods.}
      \end{cvitems}
    }
    
        \cventry
    {Blockchains,Crypto-currency} % Role
    {Goofy and Scrooge coins : Simple Crypto-currency systems.} % Title
    {} % Location
    {} % Date(s)
    {
      \begin{cvitems} % Description(s)
        \item {Designed a cryptocurrency system based on blockchain principles.}
      \end{cvitems}
    }
\newpage
%---------------------------------------------------------
\end{cventries}